Supplemental Information from:\\ \textit{Reconstructing the last known movements of one of Nature's giants}

### 2019-07-18 manuscript/PeerJ/blue-new-supplementary.tex
Fix supplementary

% figure s2
\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S1-periodograms.png}
  \caption{Fourier analysis of $\delta^{15}$N values of the full (A) and behavioural phase two only (B) and behavioural phase three only (C) components of the baleen plate. Inset values are the highest frequency spectral densities (in cm). Periodic fluctuation with a distance of 13.5cm along the baleen plate is consistently recovered in behavioural phases one and two, but not in behavioural phase three.} 
  \label{figs2}
\end{figure}

@@

  \vspace{-1cm}
\begin{figure}[!htbp]
  \centering
  \includegraphics[trim = {3cm 0 0 0}, clip]{figures/flow-diagram-model.pdf}
  %\vspace{-1.2cm}
  \linespread{0.8}
  \caption{
  Schematic structure of the agent-based model used to generate hypothetical movement tracks. 
  At the start of each simulation, max and min sea surface temperature (SST) and food availability thresholds are fixed for all individuals. Behavioural states are defined \textit{a priori} based on day of the year. Maximum movement distances under each behavioural state are defined for each individual based on a random sample from a Gaussian distribution. The model runs with a daily time step. Current location and day of simulation is noted, and the behavioural state defined. Environmental conditions (SST, food availability and depth) are sensed in the current and eight adjacent 1$^{\circ}$ grid cells. The probability of movement is sampled from a binomial distribution defined according to behavioural state and environmental conditions in the current location. The direction of movement is sampled based on discrete probabilities associated to each of the eight adjacent 1$^{\circ}$ cells, defined according to behavioural state and environmental conditions. Finally the distance moved is sampled from a Poisson distribution conditional on the maximum distance defined for each individual. The new location is then assigned from a linear vector originating at the current location with magnitude defined as the distance moved and direction as 45$^{\circ}$ increments reflecting the relative orientation of each of the eight potential adjacent cells.}
  \label{figs3}
\end{figure}

>>>>

% figure s2
\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S1-periodograms.png}
  \caption{Fourier analysis of $\delta^{15}$N values of the full (A) and behavioural phase two only (B) components of the baleen plate. Inset values are the highest frequency spectral densities (in cm). Periodic fluctuation with a distance of 13.5cm along the baleen plate is consistently recovered in behavioural phase two where the whale engaged in latitudinal migrations. Note that we do not separately graph behavioural phases one or three here because they do not show clear periodicity.} 
  \label{figs2}
\end{figure}

@@

  \vspace{-1cm}
\begin{figure}[!htbp]
  \centering
  \includegraphics[trim = {3cm 0 0 0}, clip]{figures/flowdiagrammodel.pdf}
  %\vspace{-1.2cm}
  \linespread{0.8}
  \caption{
  Schematic structure of the agent-based model used to generate hypothetical movement tracks. 
  At the start of each simulation, max and min sea surface temperature (SST) and food availability thresholds are fixed for all individuals. Behavioural states are defined \textit{a priori} based on day of the year. Maximum movement distances under each behavioural state are defined for each individual based on a random sample from a Gaussian distribution. The model runs with a daily time step. Current location and day of simulation is noted, and the behavioural state defined. Environmental conditions (SST, food availability and depth) are sensed in the current and eight adjacent 1$^{\circ}$ grid cells. The probability of movement is sampled from a binomial distribution defined according to behavioural state and environmental conditions in the current location. The direction of movement is sampled based on discrete probabilities associated to each of the eight adjacent 1$^{\circ}$ cells, defined according to behavioural state and environmental conditions. Finally the distance moved is sampled from a Poisson distribution conditional on the maximum distance defined for each individual. The new location is then assigned from a linear vector originating at the current location with magnitude defined as the distance moved and direction as 45$^{\circ}$ increments reflecting the relative orientation of each of the eight potential adjacent cells.}
  \label{figs3}
\end{figure}
